Adapting the Chumbley Score to Bullet Striations

### 2018-04-25 presentation/presentation.Rmd
spme presadds

>>>>

## Appendix

###U Statistic:

This is computed from the joint rank of all correlations of both the same and different shift samples. As given by \citet{hadler}

Null Hypothesis: If the toolmarks were not match i.e not made by the same tool.

Let $n_s$ and $n_d$ be the number of same shift and different shift windows $N = n_{s} + n_{d}$

The mann whitney U statistic is given by $U =\sum^{ns}{i=1}R{s}\left( i\right)$

with the standardized version which includes provision for rank ties

$\overline{U}= \dfrac{U-M}{\sqrt{V}}$

where prior to normalization the U-statistic has the mean as

$M = n_{s}\left(\dfrac{N+1}{2}\right)$

and variance

$V = \dfrac{n_{s}n_{d}}{N\left(N-1\right)}\left[\Sigma^{n_{s}}R_{s}\left(i\right)^{2}+\Sigma^{n_{d}}R_{d}\left(j\right)^{2}\right] -\dfrac{n_{s} n_{d}\left(N+1\right)^{2}}{4\left(N-1\right)}$
